---
title: "Google Trends Analysis in R"
author: "Olayinka Arimoro"
date: "May 4, 2021"
output: html_document
---

# Task One: Getting Started
In this task, you will import the required
packages for this project
```{r}

## 1.1: Importing required packages
library(gtrendsR)
library(dplyr)
library(ggplot2)
library(ggforce)
library(ggrepel)
library(spData)
library(tmap)
library(DT)

```

#Task Two: Getting Google trends data
In this task, we will learn how to get 
Google trends data about Covid-19
```{r}

## 2.1: Retrieve the worldwide data for 
## "covid" in the last 12 months


## 2.2: Return the names of the datasets from trends


## 2.3: Search for the keywords "covid" and 
## "vaccine" in US in the last 12 months
gtrends(keyword = c("covid","vaccine"),time = "today 12-m", geo="US")

```

#Task Three: Interest Over Time Data
In this task, we will learn how to examine 
and explore the interest over time data
```{r}

## 3.1: Return the interest over time 
## data from the trends dataset


## 3.2: Print the interest_time data


## 3.3: Return the dates with the highest number of hits


```

#Task Four: Visualize the Interest Over Time Data
In this task, we will learn how to 
visualize the interest over time data
```{r}

## 4.1: Visualize the interest over time data


## 4.2: Zoom in to check between January 1, 2021
## to April 30, 2021


```

#Task Five: Related Queries Data
In this task, we will examine and 
explore related queries to Covid
```{r}

## 5.1: Return the related queries data


## 5.2: Create a bar plot for the queries 
## most related to covid


```

#Task Six: Interest by Country Data
In this task, we will examine and 
explore the interest by country data
```{r}

## 6.1: Return the interest by country data


## 6.2: Create a variable called "countries" 
## from the world data and interest by country data


## 6.3: Create a map of the interest by countries
tm_shape(countries) +
  tm_fill("hits",
          title = "Search Interest",
          legend.reverse = T,
          id = "name_long", 
          popup.vars = c(Name = "name_long", Search.Interest = "hits",
                       Population = "pop", Life.Expectancy = "lifeExp", 
                       GDP.per.capita = "gdpPercap"))

## 6.4: Different versions of the map
tmap_mode("view") #interactive maps

## OR

tmap_mode("plot") #plot-ready maps

```

#Task Seven: Interest by City Data
In this task, we will examine and
explore the interest by city data
```{r}

## 7.1: Return the interest by city data


## 7.2: Return the top 3 cities with the highest hits


## 7.3: Return a table for the interest by city


## 7.4: Return the first 25 rows of the table


```
